Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Add Nessai citation

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up
the PE process. This includes methods that employ modern techniques such as
deep learning networks pre-trained on large collections of waveforms
\cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot}. While these avenues are promising for
standard GW problems, they rely on assumptions that may not hold for analyses
targeting additional physical effects beyond standard CBCs in GR, such as
lensing and deviations from GR, or may use approximations that do not compute
the Bayesian likelihood exactly.

>>>>

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot}. While these avenues are promising for
standard GW problems, they rely on assumptions that may not hold for analyses
targeting additional physical effects beyond standard CBCs in GR, such as
lensing and deviations from GR, or may use approximations that do not compute
the Bayesian likelihood exactly.
